Distance Sampling in \proglang{R}

### 2016-06-08 paper.Rnw
getting there...

A different form for the detection function can be specified via the \code{key=} argument to \code{ds}. For example, a hazard rate model can be fitted as:
<<label=minke-hr-cos>>=
minke_hrcos <- ds(minke, truncation = 1.5, key = "hr")
@
Here \code{ds} also fits the hazard-rate model then hazard-rate with a cosine adjustment but the AIC improvement is insufficient to select the adjustment, so the hazard-rate key-only model is returned.

>>>>

A different form for the detection function can be specified via the \code{key=} argument to \code{ds}. For example, a hazard rate model can be fitted as:
<<label=minke-hr-cos, message=TRUE>>=
minke_hrcos <- ds(minke, truncation = 1.5, key = "hr")
@
Here \code{ds} also fits the hazard-rate model then hazard-rate with a cosine adjustment but the AIC improvement is insufficient to select the adjustment, so the hazard-rate key-only model is returned.
